---
title: Predicting Wine Quality and Wine Type
author: Eric Leung
date: 2016 June 17th
output: 
  pdf_document: 
    toc: yes
bibliography: refs.bib
classoption: twocolumn
---

```{r Load Packages, echo=FALSE, message=FALSE}
# Load packages
require(ggplot2)
require(dplyr)
```

```{r Source, echo=FALSE}
source("../bin/load_data.R")
```

# Introduction

# Data

I used the Wine Quality Data Set. This data comes from Dr. Paulo Cortez and
their pursuit to predict wine quality preferences [@cortez2009modeling]. The
data was downloaded from the UCI Machine Learning Repository [@lichman2013uci].

The data analyzed included two datasets, one related to red *vinho verde* and
the other related to white *vinho verde*. Each of the two datasets contain
twelve variables, one of which was the participant's quality score for that wine
[@lichman2013uci].

The red wine dataset has `r nrow(red)` samples while the white wine dataset has
`r nrow(white)` samples. It was not clear from the reference paper on how they
collected the data besides being tested "at the official certification entity
(CVRVV)" [@cortez2009modeling].

The physicochemical variables available are:

1. fixed acidity (g(tartaric acid)/dm^3^)
2. volatile acidity (g(acetic acid)/dm^3^)
3. citric acid (g/dm^3^)
4. residual sugar (g/dm^3^)
5. chlorides (g(sodium chloride)/dm^3^)
6. free sulfur dioxide (mg/dm^3^)
7. total sulfur dioxide (mg/dm^3^)
8. density (g/cm^3^)
9. pH
10. sulphates (g(potassium sulphate)/dm^3^)
11. alcohol (vol.%)

These variables will be used in my machine learning methods.


# Methods

# Results

# Discussion

# References